Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

\begin{proof}
    Let $h$ be the full segment of $\bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ covering both endpoints of $h$. Thus, the effective horizontal segment of $\bm{t}$ (defined in Section~\ref{sec:hv:type2}), which is contained in $h'$, must also be covered by $r_{k-2}$. Hence, $\contain_{R_{k-2}}(\bm{t})$ contains $r_{k-2}$ and thus cannot be empty.
\end{proof}

>>>>

\begin{proof}
    Set $h' = \bm{t}[k-2]$. By the definition of a trimmed segment, there exists a rectangle $r_{k-2} \in R_{k-2}$ covering both endpoints of $h$. Thus, the effective horizontal segment of $\bm{t}$ (defined in Section~\ref{sec:hv:type2}) --- which must be contained in $h'$ --- must also be covered by $r_{k-2}$. Hence, $\contain_{R_{k-2}}(\bm{t})$ contains $r_{k-2}$ and thus cannot be empty.
\end{proof}
